Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-12 ICPP-19/communications.tex
Citation indicating 3 Machine Flowshop is NP-complete

	To exploit the full potential of a system it may be necessary to execute tasks on processing
	units where all of their data does not reside. A task may require all of its input data
	in local memory before starting the execution. There may be multiple tasks
	scheduled on a processing unit, which require to transfer data from the same
	memory node. Ordering data transfers for such tasks is very crucial for the
	communication-computation overlap, thus for the overall
	performance. In general, order of task execution with input
	and output data transfers can be  
	viewed as a 3-machine flowshop problem, where processing time on the first machine is 
	input data transfer time, processing time on the second machine is task execution time, 
	and processing time on the third machine is output data transfer time; and the objective is 
	to minimize the total makespan. This is a well known hard problem~\cite{NPComplete3Machine,johnson}.

@@

	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
	%%%%	done:\todo[inline]{Rewrite both paragraphs together.}
	%%	In general, order of task execution with input and output data transfers can be 
	%%	viewed as 3-machine flowshop problem, where processing time on 1st machine is 
	%%	input data transfer time, processing time on 2nd machine is task execution time, 
	%%	processing time on 3rd machine is output data transfer time and the objective is 
	%%	to minimize the total makespan. This is a well known hard problem~\cite{NPComplete3Machine,johnson}. As stated earlier, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer. Hence, problem considered in this article is simpler than general 3-machine flowshop problem.

@@

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
%%	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
	For simplicity, we assume in all of this paper that the
	amount of memory required by a task is proportional to its
	communication time, and without loss of generality we consider
	that memory size of a task is equal to its communication volume.

@@

	\begin{table}
		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				A & 0 & 0 & 5\\ \hline
				B & 4 & 4 & 3\\ \hline
				C & 1 & 1 & 6\\ \hline
				D & 3 & 3 & 7\\ \hline
				E & 6 & 6 & 0.5\\ \hline
				F & 7 & 7 & 0.5\\ \hline
			\end{tabular}
		\end{center}
		\caption{Example instance where ordering on both resources
			has to be different.}
		\label{table:different.order}
	\end{table}

@@

			\begin{tabular}{|c|c|c|c|}
				\hline
				%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
				%%				&=Comm Volume& \\ \hline
				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				A & 3 & 3 &  2\\ \hline
				B & 1 & 1 & 3\\ \hline
				C & 4 & 4 & 4\\ \hline
				D & 2 & 2 & 1\\ \hline
			\end{tabular}
			\caption{\label{tab:staticOrderExample} A task set for static order schedules.}
		\end{center}
	\end{table}

@@

			\begin{tabular}{|c|c|c|c|}
				\hline
				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				A & 3 & 3 & 2\\ \hline
				B & 1 & 1 &  6\\ \hline
				C & 4 & 4 & 6\\ \hline
				D & 5 & 5 & 1\\ \hline
			\end{tabular}
			\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.}
		\end{center}
	\end{table}

@@

			\begin{tabular}{|c|c|c|c|}
				\hline
				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				A & 4 & 4 &  1\\ \hline
				B & 2 & 2 & 6\\ \hline
				C & 8 & 8 & 8\\ \hline
				D & 5 & 5 & 4\\ \hline
				E & 3 & 3 & 2\\ \hline
			\end{tabular}
			\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
		\end{center}
	\end{table}

>>>>

	To exploit the full potential of a system it may be necessary to execute tasks on processing
	units where all of their data does not reside. A task may require all of its input data
	in local memory before starting the execution. There may be multiple tasks
	scheduled on a processing unit, which require to transfer data from the same
	memory node. Ordering data transfers for such tasks is very crucial for the
	communication-computation overlap, thus for the overall
	performance. In general, order of task execution with input
	and output data transfers can be  
	viewed as a 3-machine flowshop problem, where processing time on the first machine is 
	input data transfer time, processing time on the second machine is task execution time, 
	and processing time on the third machine is output data transfer time; and the objective is 
	to minimize the total makespan. This is a well known NP-complete problem~\cite{3machineFlowShopNPComplete}.

@@

%%	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
	%%%%	done:\todo[inline]{Rewrite both paragraphs together.}
	%%	In general, order of task execution with input and output data transfers can be 
	%%	viewed as 3-machine flowshop problem, where processing time on 1st machine is 
	%%	input data transfer time, processing time on 2nd machine is task execution time, 
	%%	processing time on 3rd machine is output data transfer time and the objective is 
	%%	to minimize the total makespan. This is a well known hard problem~\cite{NPComplete3Machine,johnson}. As stated earlier, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer. Hence, problem considered in this article is simpler than general 3-machine flowshop problem.

@@

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
	\todo[inline]{SKumar: Why not a direct statement?  For simplicity, we assume in all of this paper that the amount of memory required by a task is equal to its communication volume.}
	For simplicity, we assume in all of this paper that the
	amount of memory required by a task is proportional to its
	communication time, and without loss of generality we consider
	that memory size of a task is equal to its communication time.

@@

	\begin{table}
		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
				&=Comm Volume && \\ \hline
				A & 0 & 0 & 5\\ \hline
				B & 4 & 4 & 3\\ \hline
				C & 1 & 1 & 6\\ \hline
				D & 3 & 3 & 7\\ \hline
				E & 6 & 6 & 0.5\\ \hline
				F & 7 & 7 & 0.5\\ \hline
			\end{tabular}
		\end{center}
		\caption{Example instance where ordering on both resources
			has to be different.}
		\label{table:different.order}
	\end{table}

@@

			\begin{tabular}{|c|c|c|c|}
				\hline
				%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
				%%				&=Comm Volume& \\ \hline
%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
				&=Comm Volume && \\ \hline
				A & 3 & 3 &  2\\ \hline
				B & 1 & 1 & 3\\ \hline
				C & 4 & 4 & 4\\ \hline
				D & 2 & 2 & 1\\ \hline
			\end{tabular}
			\caption{\label{tab:staticOrderExample} A task set for static order schedules.}
		\end{center}
	\end{table}

@@

			\begin{tabular}{|c|c|c|c|}
				\hline
%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
				&=Comm Volume && \\ \hline
				A & 3 & 3 & 2\\ \hline
				B & 1 & 1 &  6\\ \hline
				C & 4 & 4 & 6\\ \hline
				D & 5 & 5 & 1\\ \hline
			\end{tabular}
			\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.}
		\end{center}
	\end{table}

@@

			\begin{tabular}{|c|c|c|c|}
				\hline
%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
				&=Comm Volume && \\ \hline
				A & 4 & 4 &  1\\ \hline
				B & 2 & 2 & 6\\ \hline
				C & 8 & 8 & 8\\ \hline
				D & 5 & 5 & 4\\ \hline
				E & 3 & 3 & 2\\ \hline
			\end{tabular}
			\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
		\end{center}
	\end{table}
